---
title: "Data Visualization"
author: "Martin"
date: "2/24/2022"
output: html_document
---
# Data Visualization (incarceration)

### Introduction 
The variable that I chose to analyze is Jail. The components under the Jail variables are composed by jail admissions, jail population, pretrial population, jurisdiction identifier, private jail jurisdiction flag, and multi-jurisdiction jail flag. After watching the Netflix documentary "13TH | FULL FEATURE", I reveal that there was reason in american history that causes the increase in jail population. Hence, I will focus on analyzing jail population. Total jail population is defined as the average daily number through December 31 of a given year. Jail population estimates are dis-aggregated by race and gender as well as by jurisdiction.

```{r}
source("~/Desktop/Info/a3-martinma0104/source/analysis.R")

Stat_with_most_population <- county_level %>%
  filter(total_pop == max(total_pop, na.rm=TRUE)) %>%
  pull(state)

Stat_with_least_population <- county_level %>%
  filter(total_pop == min(total_pop, na.rm=TRUE)) %>%
  pull(state)
```

By evaluating the data sets I found out that the state with the highest jail population is CA and AK is the state with the least jail population. 

```{r}
Year_with_most_population <- county_level %>%
  filter(total_pop == max(total_pop, na.rm=TRUE)) %>%
  pull(year)

Year_with_least_population <- county_level %>%
  filter(total_pop == min(total_pop, na.rm=TRUE)) %>%
  pull(year)
```

The year with the most jail population is 2016. There were many years with the least population, which are 1970, 1971, 1972. 

The graph shows the Jail population in 2018. Each bar represents a county. The y axis is the number of people in jail. We can see that there are huge differences of jail population in each county.

### Trends over time charts
The Charts shows the trend of jail population in three counties from 2008 to 2018. The y-axis is total jail population and the x-axis is time. The line graph can clearly shows the trend, which is an increasing trend. LA has the most jail population within the three counties. San Francisco has the least jail population within the three counties. 

```{r}
source("~/Desktop/Info/a3-martinma0104/source/1analysis.R")
```


### Comparison 

```{r echo=FALSE}
library(readxl)
library(ggplot2) 
library(plotly)
library(hrbrthemes)
Info_data1 <- read_excel("~/Desktop/Info_data1.xlsx")
Info_data1$Date <- as.Date(Info_data1$Date)

Info_data1 %>% 
  ggplot( aes(x=Date, y=male_pop_15to64)) +
  geom_line(color="#69b3a2") +
  ylim(0,20000) +
  theme_ipsum()
```
```{r echo=FALSE}
Info2 <- read_excel("~/Desktop/Info2.xlsx")
Info2$Date <- as.Date(Info2$Date)

Info2 %>% 
  ggplot( aes(x=Date, y=female_pop_15to64)) +
  geom_line(color="#69b3a2") +
  ylim(0,20000) +
  theme_ipsum()
```


The female jail population and male population are having the same trend, which is increasing from 1970 to 2018. The population of female is bit higher than the male population. 

### Mapping

```{r echo=FALSE}
library(maps)
library(tmap) 
library(leaflet) 
library(ggplot2) 
library(dplyr)
library(tidyverse)
library(ggmap)

map <- get_stamenmap(
  bbox = c(left = -133.77, bottom = 8.32, right = -51.33, top = 62.02),
  maptype = "toner",
  zoom = 4
)

ggmap(map)
```

